Binary companions of red giant stars in \apogee\ \DR

### 2018-03-02 paper/1-catalog/twoface-catalog.tex
Figure captions

% Notebook: "HighK"
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-0}
\end{center}
\caption{%
TODO
\label{fig:highK-0}
}
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-1}
\end{center}
\caption{%
TODO
\label{fig:highK-1}
}
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{lowK-0}
\end{center}
\caption{%
TODO
\label{fig:lowK-0}
}
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{lowK-1}
\end{center}
\caption{%
TODO
\label{fig:lowK-1}
}
\end{figure}

>>>>

% Notebook: "HighK"
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-0}
\end{center}
\caption{%
Examples of stars in our high-$K$ sample, i.e. stars that likely have companions
(see \sectionname~\ref{sec:catalog-confident}), with different numbers of
visits.
Left panels show the data (black markers, error bars are the visit velocity
uncertainties) with 128 random orbits from the \nposterior\ posterior samples
under-plotted (grey lines); The \texttt{APOGEE\_ID} of each target and the
number of visits that pass our quality cuts, $N$, are indicated on each panel.
Right panels show the \nposterior\ posterior samples visualized in
period--eccentricity space.
In most cases, despite confidently having companions based on the RV amplitude,
the permitted orbit fits are highly multimodal.
\label{fig:highK-0}
}
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-1}
\end{center}
\caption{%
Continuation of \figurename~\ref{fig:highK-0}.
\label{fig:highK-1}
}
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{lowK-0}
\end{center}
\caption{%
Same as \figurename~\ref{fig:highK-0}, but for stars in the low-$K$ sample, i.e.
stars that have undetected or no companions.
\label{fig:lowK-0}
}
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{lowK-1}
\end{center}
\caption{%
Continuation of \figurename~\ref{fig:lowK-0}.
\label{fig:lowK-1}
}
\end{figure}
